Fission product decay chain equilibria in \zirconia

### 2019-01-25 manuscript.tex
Add Xenon explanation

>>>>

\ch{Xe_{O}^{**}} and \ch{Xe_{Zr}^{''''}} have defect volumes of 9.02 and 115.50 \r{A}$^{3}$ respectively. Following from the decay of iodine, the defect volume on the oxygen site will fall from 29.90 \r{A}$^{3}$, while the defect volume on the zirconium site increases from 87.07 \r{A}$^{3}$. The defect volume reduction on the oxygen site can be attributed to the charge state changing from -1 to 0 (i.e. \ch{I_{O}^{*}} to \ch{Xe_{O}^{**}}), resulting in a smaller defect. The opposite is true for the zirconium site, where the charge state changes from +1 to 0 (\ch{I_{Zr}^{'''}} to \ch{Xe_{Zr}^{''''}}).
